Self-test prime dimensional EPR pairs with constant alphabet

### 2019-04-15 Draft/draft.tex
Honghao: trying to self-test the 2 EPR pairs

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}

@@

In Slofstra's seminal work~\cite{slofstra2017} embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be reproduced from the
combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
our work.
\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables, $n_r := 17r + 73$, 
	and the number of equations, $m_r =15r + 61$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $n_r$ and $m_r$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
at the beginning of a section, but you shouldn't be making
such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
meaning.}
As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

@@

%-----------------------------------------------------------------
\subsection{The correlation $C(\dr{r})$}
%-----------------------------------------------------------------
Recall that the linear system game $\LS_r$ has $n_r$ variables and $m_r$ equations.
In game $\G(\dr{r})$, 
Alice receives $x \in \{1,\dots m_r+3 \}$ and Bob receives
$y \in \{1,\dots,n_r+1\}$. We follow the previous structure by first give intuition about how they should
behave in this game. The correlation can be easily extracted from the behaviour list below.
\begin{itemize}
	\item When $x \in \{1,\dots m_r\}$ and $y \in \{1, \dots n_r\}$, they should win the 
	linear system game $\LS_r$ perfectly;
	\item when $x \in \{m_r+1, m_r+2, m_r+3\}$ and $y \in \{1, 2, n_r+1\}$, they should follow the
	optimal correlation of the test $\CHSH_X$, where 
	\begin{align}
		&\ast_A = m_r+1, \quad 1_A = m_r+2,\quad 2_A = m_r+3,\\
		&\ast_B = n_r+1,\quad 1_B = 1, \quad 2_A = 2,
	\end{align}
	are the inputs for the game $\CHSH_X$
	(The intuition behind is that $B_1B_2 = X$.);
	\item otherwise, their behaviour is irrelevant.
\end{itemize}
Note that the dimension $\dr{r}$ is defined in the rules of $\CHSH_X$.

@@

\textbf{The ideal strategy for $\LS_r$}.
We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n_r(x)$.
In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
\begin{align}
	G_r(x) = \ip{ \{x_i\}_{i=1}^{n_r(x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
\end{align}
where details of $C_r$ can be found in the appendices. 
Note that the relation $uxu^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
Building on $\Psi_1$, we can construct 
the representation $\Psi_{\LS_r}$ for the solution group $\Gamma(\LS_r)$.

Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
%\begin{align}
%	B_1 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
%	B_2 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
%\end{align}
\begin{align}
	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
\end{align}
It can be checked that $X = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
The relation $uxu^{-1} = x^r$ and $X$ determine that 
\begin{align}
	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
\end{align}
\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
The first step of the embedding procedure in the proof of \cref{prop:embed} requires
the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
The commutation relation can be checked as follows,
\begin{align}
	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}}.
\end{align}
Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
\begin{align*}
	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
\end{align*}
Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
\begin{align}
	rx \equiv d \pmod{d}
\end{align}
Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
\begin{align}
	UB_2U\ct = B_2.
\end{align}

@@

Next, we consider the representation $\Psi_2$ for the group 
\begin{align*}
	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots n_r(x) \\
	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r}.
\end{align*}
The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
$\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n_r(x)$.
Building on $\Psi_1$, we have $\Psi_2(x_i) = \Psi_1(x_i) \oplus \Psi_1(x_i)$, then
$y_i$, $z_i$, $w_i$ and $f$ are mapped to
\begin{align*}
\Psi_2(y_i) = 
\begin{pmatrix}
\Psi_1(x_i) & 0\\
0 & \1
\end{pmatrix},
&&
\Psi_2(z_i) \to
\begin{pmatrix}
\1 & 0\\
0 & \Psi_1(x_i)
\end{pmatrix},
\\
\Psi_2(w_i) = 
\begin{pmatrix}
0 & \Psi_1(x_i)\\
\Psi_1(x_i) & 0
\end{pmatrix},
&&
\Psi_2(f) \to
\begin{pmatrix}
0 & \1\\
\1 & 0
\end{pmatrix}.
\end{align*}
It can be easily checked that the order-$2$ generators are mapped to order-$2$ operators and
the relations satisfied by the generators are preserved.
For each $g_{jk}$ where $(i,j,k) \in C_r$, $\Psi_2(g_{jk}) = \Psi_2(y_j)\Psi_2(z_k)$ following
their defining relations.

The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n_r(x)}
\cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
in $G_r(x,y,z,w)$ can be found in the appendices. Now we define the representation $\Psi_{\LS_r}$ of
$\Gamma(\LS_r)$. For any generator $a \in \{x_i, w_i, y_i, z_i\}_{i=1}^{n_r(x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r}$,
\begin{align}
	\Psi_{\LS_r}(a) = \Psi_2(a) \oplus \Psi_2(a) = \Psi_1(a)^{\oplus 4}.
\end{align}
For generators $\{y_{F_j,k}\}_{k=1}^7\}_{j=1}^{n_r(x)}$,
\begin{align*}
	\Psi_{\LS_r}(y_{F_j,1}) = 
	\begin{pmatrix}
		0 & \Psi_2(f) \\
		\Psi_2(f) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,2}) = 
	\begin{pmatrix}
		0 & \1\\
		\1 & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,3}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_j) \\
		\Psi_2(y_j) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,4}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_jf) \\
		\Psi_2(fy_j) & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,5}) = 
	\begin{pmatrix}
		 \Psi_2(fy_jf) & 0\\
		  0 & \Psi_2(f)
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,6}) = 
	\begin{pmatrix}
		 \Psi_2(y_jz_j) & 0\\
		 0 & \1
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,7}) = 
	\begin{pmatrix}
		 \Psi_2(y_j) & 0\\
		 0 & \Psi_2(z_j)
	\end{pmatrix}.
\end{align*}
For generators $\{\{y_{K,k}\}_{k=1}^7\}_{K=(k_1,k_2,k_3) \in C_r}$,
\begin{align*}
	\Psi_{\LS_r}(y_{K,1}) = 
	\begin{pmatrix}
		0 & \Psi_2(w_{k_1}) \\
		\Psi_2(w_{k_1}) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,2}) = 
	\begin{pmatrix}
		0 & \1\\
		\1 & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,3}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_{k_2}) \\
		\Psi_2(y_{k_2}) & 0
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,4}) = 
	\begin{pmatrix}
		0 & \Psi_2(y_{k_2}w_{k_1}) \\
		\Psi_2(w_{k_1}y_{k_2}) & 0
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,5}) = 
	\begin{pmatrix}
		 \Psi_2(w_{k_1}y_{k_2}w_{k_1}) & 0\\
		  0 & \Psi_2(w_{k_1})
	\end{pmatrix},
	&&
	\Psi_{\LS_r}(y_{F_j,6}) = 
	\begin{pmatrix}
		 \Psi_2(y_{k_2}z_{k_3}) & 0\\
		 0 & \1
	\end{pmatrix},\\
	\Psi_{\LS_r}(y_{F_j,7}) = 
	\begin{pmatrix}
		 \Psi_2(y_{k_2}) & 0\\
		 0 & \Psi_2(z_{k_3})
	\end{pmatrix}.
\end{align*}

>>>>

\newcommand{\CHSH}{CHSH^{(d)}}
\newcommand{\MS}{MS}
\newcommand{\SVT}{SVT}
\newcommand{\EPR}[1]{\Sigma^{(#1)}}
\newcommand{\paulix}{\sigma_x}
\newcommand{\pauliz}{\sigma_z}
\newcommand{\G}{G}
\newcommand{\LS}{LS}
\newcommand{\tA}{\tilde{A}}
\newcommand{\tB}{\tilde{B}}
\newcommand{\tX}{\tilde{X}}
\newcommand{\tZ}{\tilde{Z}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\tx}{\tilde{x}}
\newcommand{\tpsi}{\tilde{\psi}}
\newcommand{\tri}{\Delta}
\newcommand{\lB}{\overline{B}}
\newcommand{\dr}[1]{d^{(#1)}}
\newcommand{\nr}{n(r)}
\newcommand{\mr}{m(r)}

@@

In Slofstra's seminal work~\cite{slofstra2017} embeds the group
\begin{align}
	K = \ip{ x,y,a,b:a^2=b^2=e, ab=ba, yay^{-1} = a, yby^{-1} = ab, xyx^{-1}=y^2}
\end{align}
into a linear system game such that the relations in the definition of $K$ can be reproduced from the
combination of the equations of the linear system game. The special relation $xyx^{-1} = y^2$ inspired 
our work.
\hf{We generalize this relation and make he solution group of $\LS_r$ the embedding of the 
following group}
\begin{align}
	\Pg_r= \langle u, o : uou^{-1} = o^r \rangle, \text{ for } r \in \N.
\end{align}
In other words, relations in the presentation of the solution group of $\LS$ can be combined to derive the
relation $uou^{-1} = o^r$.  
\begin{proposition}
	\label{prop:embed}
	The group $\Pg_r$ can be embedded into a linear system game $\LS_r$ over $\Z_2$,
	with the numbers of variables, $\nr := 17r + 73$, 
	and the number of equations, $\mr =15r + 61$, where each equation involves $3$ variables.
	\carl{You need to make this a more precise statement.  (It sounds as if you're saying 
	that the numbers of variables and equations is independent of $r$, which I'm pretty sure is not true.)}
\end{proposition}
The process of embedding $\Pg_r$ into the solution group of $\LS$ follows the recipe given in the proofs of
Proposition~$4.8$, Lemma~$4.4$ and Proposition $4.2$ of Ref.~\cite{slofstra2017}.
The order of applying the results is the reverse of the order they are presented in Ref.~\cite{slofstra2017}.
We give details of this embedding process in \cref{sec:power2} for $r = 2$, \cref{sec:power3} for $r = 3$, 
and \cref{sec:power5} for $r = 5$.

In the later parts of the paper, we use $\nr$ and $\mr$ to refer to the size of $\LS_r$.
The key feature of this embedding is that $\LS_r$ has constant-sized input-output alphabet
even if the generators $u$ and $x$ have arbitrary order. 
The product of the generators $x_1$ and $x_2$ from the solution group of $\LS_r$ plays the role 
of the generator $x$ in $\Pg_r$ and the product of the generators $x_3$ and $x_4$ plays the role
of the generator $u$ in $\Pg_r$.   \carl{It's reasonable to make a couple informal statements
at the beginning of a section, but you shouldn't be making
such vague statements at this point.  Everything said at this point in the section should have a precise mathematical
meaning.}
As shown in \cref{sec:power2}, \cref{sec:power3} and \cref{sec:power5}, 
$x_1$,$x_2$,$x_3$ and $x_4$ satisfy the relation
\begin{align}
	(x_3x_4)(x_1x_2)(x_4x_3) = (x_1x_2)^r.
\end{align}
Hence the perfect quantum strategy $(\ket{\psi}, \{A_i, B_i\}_{i=1}^n)$ should satisfy 
the key relation that 
\begin{align}
	(A_3A_4) (A_1A_2)(A_4A_3) \ket{\psi} = (A_1A_2)^r\ket{\psi}, 
\end{align}
and similarly on Bob's side.
If we denote the unitary corresponding to the generator $u$ of $\Pg_r$ by $U$ and the unitary
corresponding to $x$ by $X$, then $U = A_3A_4$, $X= A_1A_2$, and 
$UXU\ct \ket{\psi} = X^r \ket{\psi}$.
The special property of $U$ and $X$ is summarized in the following lemma.

@@

%-----------------------------------------------------------------
\subsection{The correlation $C(\dr{r})$}
%-----------------------------------------------------------------
Recall that the linear system game $\LS_r$ has $\nr$ variables and $\mr$ equations.
In game $\G(\dr{r})$, 
Alice receives $x \in \{1,\dots \mr+3 \}$ and Bob receives
$y \in \{1,\dots,\nr+1\}$. We follow the previous structure by first give intuition about how they should
behave in this game. The correlation can be easily extracted from the behaviour list below.
\begin{itemize}
	\item When $x \in \{1,\dots \mr\}$ and $y \in \{1, \dots \nr\}$, they should win the 
	linear system game $\LS_r$ perfectly;
	\item when $x \in \{\mr+1, \mr+2, \mr+3\}$ and $y \in \{1, 2, \nr+1\}$, they should follow the
	optimal correlation of the test $\CHSH_X$, where 
	\begin{align}
		&\ast_A = m_r+1, \quad 1_A = m_r+2,\quad 2_A = m_r+3,\\
		&\ast_B = \nr+1,\quad 1_B = 1, \quad 2_A = 2,
	\end{align}
	are the inputs for the game $\CHSH_X$
	(The intuition behind is that $B_1B_2 = X$.);
	\item otherwise, their behaviour is irrelevant.
\end{itemize}
Note that the dimension $\dr{r}$ is defined in the rules of $\CHSH_X$.

@@

\textbf{The ideal strategy for $\LS_r$}.
We denote the number of generators labelled by $x_i$ in $\LS_r$ by $n(r,x)$.
In order to construct a representation of $\Gamma(\LS_r)$, we first construct a representation, $\Psi_1$ for the group 
\begin{align}
	G_r(x) = \ip{ \{x_i\}_{i=1}^{n(r,x)}: x_i^2 = e, x_i x_j x_i = x_k \text{ for all } (i,j,k) \in C_r},
\end{align}
on the vector space $W_{d-1} = \spn(\{ \ket{x_j} \}_{j=1}^{d-1})$,
where details of $C_r$ can be found in the appendices. 
Note that the relation $uou^{-1} = x^r$ is embedded in the conjugation relations in $C_r$.
Building on $\Psi_1$, we can construct 
the representation $\Psi_{\LS_r}$ for the solution group $\Gamma(\LS_r)$.

Since Bob gets the same symbols $1$ and $2$ in different sub-tests, 
the observables $A_1 = B_1 = \Psi_1(x_1)$ and $A_2 = B_2 = \Psi_1(x_2)$ are extended from $B_1|_V$ and $B_2|_V$ as follows
%\begin{align}
%	B_1 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_k}{x_{d-k}} + e^{-ik\pi/2d}\ketbra{x_{d-k}}{x_k}\right)\\
%	B_2 = \ketbra{x_0}{x_0} + 
%	\sum_{k=1}^{(d-1)/2}\left( e^{ik\pi/2d}\ketbra{x_{d-k}}{x_k} + e^{-ik\pi/2d}\ketbra{x_{k}}{x_{d-k}}\right)
%\end{align}
\begin{align}
	A_1 = B_1 = \Psi_1(x_1) &= \sum_{k=1}^{(d-1)/2}\left( \omega_d^k\ketbra{x_k}{x_{d-k}} + \omega_d^{-k}\ketbra{x_{d-k}}{x_k}\right)\\
	A_2 = B_2 = \Psi_1(x_2) &= \sum_{k=1}^{(d-1)/2}\left(\ketbra{x_{d-k}}{x_k} + \ketbra{x_k}{x_{d-k}}\right).
\end{align}
It can be checked that $O = \Psi_1(x_1x_2) = \sum_{i \in \Zd} \omega_d^i \ketbra{x_i}{x_i}$ 
The relation $uou^{-1} = x^r$ and the form of $O$ determine that 
\begin{align}
	U =\Psi_1(u) = \Psi_1(x_3x_4) =  \sum_{i \in \Zd} \ketbra{x_{r^{-1}i}}{x_i},
\end{align}
\hf{where $r^{-1}$ is the multiplicative inverse of $r$ in $\Zd$.
All the multiplications done on the label $i$ of the state $\ket{x_i}$ are within the group $\Zd$.}
The first step of the embedding procedure in the proof of \cref{prop:embed} requires
the commutativity between $U$ and $B_2$, so we prove the commutation relation first and
then give $\Psi_1(x_3)$ and $\Psi_1(x_4)$.
The commutation relation can be checked as follows,
\begin{align}
	UB_2U\ct = \sum_{i=1}^{d-1} U\ketbra{x_i}{x_{d-i}}U\ct = \sum_{i=1}^{d-1} \ketbra{x_{r^{-1} i}}{x_{r^{-1}(d-i)}} =B_2.
\end{align}
%Let $i_1 = i r^{-1} \in \Zd$ and $i_2  = r^{-1} (d-i) \in \Zd$, then
%\begin{align*}
%	r(i_1 + i_2) \equiv  i + (d-i) \equiv d \pmod{d} .
%\end{align*}
%Let $i_1 + i_2= x \in \{2, 3 \dots 2d-2\}$, then
%\begin{align}
%	rx \equiv d \pmod{d}
%\end{align}
%Since $d$ is an odd prime number and $r < d$, then $r$ cannot divide $d$ and the only valid value of $x$ is $d$.
%Hence, conjugation by $U$ will transform $\ketbra{x_i}{x_{d-i}}$ into another term of the same form.
%Now suppose for some $1 \leq i < i' \leq d-1$ and $U\ketbra{x_i}{x_{d-i}}U\ct = U\ketbra{x_{i'}}{x_{d-i'}}U\ct$,
%it means that in $\Zd$, $i r^{-1} = i' r^{-1}$ and $i = i'$, which contradicts the fact that $i \neq i'$.
%What we have shown so far is that conjugation by $U$ only permutes the terms of $B_2$, so
%\begin{align}
%	UB_2U\ct = B_2.
%\end{align}

@@

Next, we consider the representation $\Psi_2$ for the group 
\begin{align*}
	G(x,y,z,w) = \ip{ \{x_i, w_i, y_i, z_i\}_{i=1}^{n(r,x)}, f, \{g_{jk}\}_{(i,j,k) \in C_r} :&\text{all elements are of order $2$},\\
	&x_i = y_iz_i = fw_i,\; fy_if =z_i \text{ for } i= 1 \dots \nr(x) \\
	&g_{jk}y_j z_k = e,\; w_iy_jw_i = z_k \text{ for all } (i,j,k)\in C_r},
\end{align*}
on the vector space $W_2 \x W_{d-1}$,
where $W_2 = \spn\{ \ket{x_1}, \ket{x_2}\}$.
Note that the choice of the basis states of $W_2$ is arbitrary.
On $W_2$, we define 
\begin{align}
	\1_{W_2} = \ketbra{x_1}{x_1} + \ketbra{x_2}{x_2}, && X_{W_2} = \ketbra{x_1}{x_2} + \ketbra{x_2}{x_1}.
\end{align}
Another property that we should note is that from the presentation, we can deduce that for all $i = 1 \dots n(r,x)$, 
\begin{align}
	fx_i fx_i = f (fw_i) f (fw_i) = w_i w_i = e,
\end{align}
so $f$ commutes with $x_i$ for all $i$.
The representation $\Psi_2$ of $G(x,y,z,w)$ should satisfy the condition that for each $x_i$, 
$\Psi_2(x_i) = \Psi_2(y_i)\Psi_2(z_i) = \Psi_2(f)\Psi_2(w_i)$. We demonstrate how this representation is constructed 
for $x_i$, $y_i$, $z_i$, $w_i$ and $f$ where $i = 1 \dots n(r,x)$.
Building on $\Psi_1$, we have $\Psi_2(x_i) = \1_{W_2} \x \Psi_1(x_i)$, then
$y_i$, $z_i$, $w_i$ and $f$ are mapped to
\begin{align*}
&\Psi_2(y_i) = \ketbra{x_1}{x_1} \x \Psi_1(x_i) + \ketbra{x_2}{x_2} \x \1_{W_{d-1}} \\
&\Psi_2(z_i) =\ketbra{x_1}{x_1} \x \1_{W_{d-1}} + \ketbra{x_2}{x_2} \x \Psi_1(x_i) \\
&\Psi_2(w_i) =  X_{W_2} \x \Psi_1(x_i)\\
&\Psi_2(f) = X_{W_2} \x \1_{W_{d-1}}.
\end{align*}
It can be easily checked that the order-$2$ generators are mapped to order-$2$ operators and
the relations satisfied by the generators are preserved.
For each $g_{jk}$ where $(i,j,k) \in C_r$, 
\begin{align}
\Psi_2(g_{jk}) = \ketbra{x_1}{x_1} \x \Psi_1(x_j) + \ketbra{x_2}{x_2} \x \Psi_1(x_k).
\end{align}

The group $G_r(x,y,z,w)$ is embedded in $\Gamma(\LS_r)$ by replacing the conjugacy relations 
by linear relations. The new generators are $\{\{y_{F_j,k}\}_{k=1}^6\}_{j=1}^{n(r,x)}
\cup \{\{y_{K,k}\}_{k=1}^7\}_{K \in C_r}$. How the new linear relations can embed the conjugacy relations 
in $G_r(x,y,z,w)$ can be found in the appendices. 
The relations that we should pay attention to are
\begin{align}
	fy_{F_j,1}y_{F_j,2} =  e, && y_j y_{F_j,2}y_{F_j,3} = e \text{ for } j = 1 \dots n(r,x),
\end{align}
which imply that $y_{F_j, 2}$ commutes with $f$ and $y_j$.
Since $z_j = fy_jf$, $y_{F_j, 2}$ commutes with $z_j$ too.
We also know that $x_j = y_jz_j$, so we can conclude that $y_{F_j, 2}$ commutes with $x_j$.
